Predicting Sales Level for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-08 paper.tex
completing the SoA

Reliable sales prediction can enhance the whole production process for different companies involved in manufacturing, marketing and trading.

@@

Due to the difficulty this problem represents when forecasting sales of new 
products, some authors have proposed using different data mining methods, such as
data clustering and fuzzy neural networks \cite{Chang2009}  or
extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
In this sense, several authors have proposed using ensemble of models for sales forecasting, 
as in \cite{ChiJie2012}, where a hybrid forecasting model integrates ensemble 
empirical model decomposition and extreme learning machine to develop an effective 
forecasting model for computer products sales.
Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach 
for better handling of seasonal changes and fluctuations in consumer demands,
while Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller 
and artificial neural network for sales forecasting in printed circuit board industry.
Another authors have faced the problem of sales forecasting in textile-apparel 
fashion industry (a very similar issue to the new book publishing problem) 
using a clustering method together with decision trees, as in \cite{SThomassey2014},  or
a forecasting method based on extreme machine learning with adaptive metrics of inputs \cite{Xia2012}.

% TODO

>>>>

Reliable sales prediction can enhance the whole production process for different 
companies involved in manufacturing, marketing and trading.
Moreover, in some real-world cases, such as consumer electronics, fashion products and books,
new products are presented/launched every season; thus, accurate sales forecasting 
models could help in marketing campaigns.

@@

Due to the difficulty this problem represents when forecasting sales of new 
products, some authors have proposed using different data mining methods, such as
data clustering and fuzzy neural networks \cite{Chang2009}  or
extreme learning machine with adaptive metrics of inputs \cite{Xia2012}.
In this sense, several authors have proposed using ensemble of models for sales forecasting, 
as in \cite{ChiJie2012}, where a hybrid forecasting model integrates ensemble 
empirical model decomposition and extreme learning machine to develop an effective 
forecasting model for computer products sales.
Also, Meulstee et al. \cite{Meulstee2008} developed an ensemble learning approach 
for better handling of seasonal changes and fluctuations in consumer demands,
while Chang et al. \cite{Chang2006715} integrated a fuzzy logic controller 
and artificial neural network for sales forecasting in printed circuit board industry.
Another authors have faced the problem of sales forecasting in textile-apparel 
fashion industry (a very similar issue to the new book publishing problem) 
using a clustering method together with decision trees, as in \cite{SThomassey2014},  or
a forecasting method based on extreme machine learning with adaptive metrics 
of inputs \cite{Xia2012}.
Ching et al. \cite{ChingChin2010} use a decision-support system to classify new 
products (tea, cosmetics and soft drink) based on their sales patterns, assuming 
that products in the same class would follow a similar sales pattern. 
In any case, the proposed system can not deal with qualitative 
data related to the products.

Finally, in those problems where historical data are available, authors have 
proposed applying classical time series forecasting methods.
In \cite{Chang2009} a hybrid model integrating K-Means and fuzzy neural networks 
to forecast the future sales of a printed circuit board is proposed.
Recent works propose take advantage of information extracted from online reviews, 
such as in \cite{ChernWSF15} where an analysis on historical data throughout online 
reviews, reviewer characteristics, and review influences to understand how 
electronic `word-of-mouth' influences product sales is presented.
Similar works propose take advantage of information published on specialized 
blogs \cite{Moon2010ICSSSM,Moon2010ICEC}, having confirmed relationships between 
the number of blog references and book sales, at the time that different sales 
patterns have been observed by analysing books in series (the first book published 
takes the longest period to achieve every single sales scale, while the second book 
takes the second longest period, and so on).
In these cases, sales forecasting problems can be carried out thanks to a big 
amount of online reviews and historical data.

This paper continues our work on the prediction of sales of a new product for 
which no historical data are available, and where the classical forecasting methods 
based on time-series are not adequate.
In this sense, in \cite{Castillo2016books} the main factors influencing sales where 
analyzed in order to create a tool, based on several regression methods, that the 
publisher can use to decide how many books should be printed.

In this paper we address the problem of new book sales prediction using cost-sensitive ensemble methods.
% TODO: complete this paragraph.
